DRAFT Example Kitsap County Pedestrian Facilities Metrics/Evaluation Report

### 2022-10-08 child_single_geo.Rmd
handles adding points when they exist

this_geo <- st_as_sf(loop_df) %>% filter(tomatch == "{{current_geo}}") 
if (!is.na(st_crs(this_geo)$epsg)) {
  ncdf <- st_transform(ncdf, st_crs(this_geo)$epsg)
  nc_sw_sh <- st_transform(nc_sw_sh, st_crs(this_geo)$epsg)
}
this_roads <- st_intersection(ncdf, st_buffer(this_geo,0))
this_sw_sh <- st_intersection(nc_sw_sh, st_buffer(this_geo,0))

@@

```{r, eval=has_both}
p1 <- kitsap +
  geom_sf(data = this_geo, aes(fill = 1), alpha = 0.5, show.legend = FALSE) +
  geom_sf(data = this_roads, aes(color = 1), color = "#999999", alpha = 0.5) +
  geom_sf(data = this_sw_sh, aes(color = as.factor(TYPE)), show.legend = "line") + 
  sw_sh_col +
  theme_void() +
  labs(title = paste("Map for","{{current_geo}}"),
       caption = "Data source: Kitsap GIS - data in development",
       color = "Pedestrian Facilities")

r <- ggplot() +
  geom_sf(data = this_geo, aes(fill = 1), alpha = 0.4, lwd = 0, show.legend = FALSE) +
  geom_sf(data = this_roads, aes(color = 1), color = "#999999", alpha = 0.5) + 
  geom_sf(data = filter(this_sw_sh, SIDE_OF_RO == "RIGHT"), aes(color = as.factor(TYPE))) +
  sw_sh_col +
  labs(title = "Right",
       color = "Pedestrian Facilities") +
  theme_void()

l <- ggplot() +
  geom_sf(data = this_geo, aes(fill = 1), alpha = 0.4, lwd = 0, show.legend = FALSE) +
  geom_sf(data = this_roads, aes(color = 1), color = "#999999", alpha = 0.5) + 
  geom_sf(data = filter(this_sw_sh, SIDE_OF_RO == "LEFT"), aes(color = as.factor(TYPE))) +
  sw_sh_col +
  labs(title = "Left",
       color = "Pedestrian Facilities") +
  theme_void()

>>>>

this_geo <- st_as_sf(loop_df) %>% filter(tomatch == "{{current_geo}}")

if (!is.na(st_crs(this_geo)$epsg)) {
  ncdf <- st_transform(ncdf, st_crs(this_geo)$epsg)
  nc_sw_sh <- st_transform(nc_sw_sh, st_crs(this_geo)$epsg)
}
this_roads <- st_intersection(ncdf, st_buffer(this_geo,0))
this_sw_sh <- st_intersection(nc_sw_sh, st_buffer(this_geo,0))

@@

```{r, eval=has_both}
 # should we test for points?
the_points <- c()
if (exists("the_schools")) { the_points <- append(the_points, "the_schools")} 
if (exists("the_libraries")) { the_points <- append(the_points, "the_libraries")} 
if (exists("the_transits")) { the_points <- append(the_points, "the_transits")} 
check_points <- ifelse(length(the_points) > 0, T, F)
has_point = FALSE # start with false
```

```{r, eval=has_both & check_points}
  # see if this geo has a point (is it an area around a place, like a school)

if (length(which(eval(as.symbol(the_points)) == this_geo$tomatch)) !=0) {
  # we need to figure out which one
  has_point = TRUE
  tr <- which(eval(as.symbol(the_points)) == this_geo$tomatch)
  if (tr <= length(the_schools)) { # it is a school
    this_point <- st_as_sf(pub_schools) %>%
      filter(NAME == this_geo$tomatch)
  } else if (tr > length(the_schools) & 
             tr <= length(the_schools + length(the_libraries))) { # library
    this_point <- st_as_sf(libraries) %>%
      filter(NAME == this_geo$tomatch)
  } else { #transit
    this_point <- st_as_sf(transit_cp) %>%
      filter(NAME == this_geo$tomatch)
  }
}

```{r, eval=has_both, fig.align = "center", out.width = '100%'}
p1 <- kitsap +
  geom_sf(data = this_geo, aes(fill = 1), alpha = 0.5, show.legend = FALSE) +
  geom_sf(data = this_roads, aes(color = 1), color = "#999999", alpha = 0.5) +
  geom_sf(data = this_sw_sh, aes(color = as.factor(TYPE)), show.legend = "line") + 
  sw_sh_col +
  theme_void() +
  labs(title = paste("Map for","{{current_geo}}"),
       caption = "Data source: Kitsap GIS - data in development",
       color = "Pedestrian Facilities")

r <- ggplot() +
  geom_sf(data = this_geo, aes(fill = 1), alpha = 0.4, lwd = 0, show.legend = FALSE) +
  geom_sf(data = this_roads, aes(color = 1), color = "#999999", alpha = 0.5) + 
  geom_sf(data = filter(this_sw_sh, SIDE_OF_RO == "RIGHT"), aes(color = as.factor(TYPE))) +
  {if(has_point) geom_sf(data = this_point, 
                         aes(color = 1), color = "black", show.legend = FALSE)} +
  sw_sh_col +
  labs(title = "Right",
       color = "Pedestrian Facilities") +
  theme_void()

l <- ggplot() +
  geom_sf(data = this_geo, aes(fill = 1), alpha = 0.4, lwd = 0, show.legend = FALSE) +
  geom_sf(data = this_roads, aes(color = 1), color = "#999999", alpha = 0.5) + 
  geom_sf(data = filter(this_sw_sh, SIDE_OF_RO == "LEFT"), aes(color = as.factor(TYPE))) +
  {if(has_point) geom_sf(data = this_point, 
                         aes(color = 1), color = "black", show.legend = FALSE)} +
  sw_sh_col +
  labs(title = "Left",
       color = "Pedestrian Facilities") +
  theme_void()
